---
title: "README"
author: "Peter Meißner"
date: "`r Sys.time()`"
output: 
  html_document: 
    keep_md: yes
    number_sections: yes
    toc: yes
---

# STATUS: 

**UNDER DEVELOPMENT**



```{r, include=FALSE}
library(robotstxt)
```

# Installation and Start

```{r, eval=FALSE}
devtools::install_github("petermeissner/robotstxt")
```



# Documentation

```{r}
?robotstxt
```

# Example Usage 

Loading the package and dplyr/magrittr for neater code  ... 

```{r}
library(robotstxt)
library(dplyr)
```

## The Object Oriented Style

Initializing a new instance of the robotstxt class ... 
```{r}
rt_wikipedia <- robotstxt$new(domain="wikipedia.org")

rt_wikipedia
```


Having a look a some fields (the data stored inside the object) ... 

... the domain for which the permissions apply ... 

```{r}
rt_wikipedia$domain
```

... the actual text of the robots.txt file ... 

```{r}
rt_wikipedia$text %>% 
  substring(1, 400) 
```

... bots mentioned by name ...

```{r}
rt_wikipedia$bots
```

Checking if some any bot might access the root path ... 
```{r}
# checking for access permissions
rt_wikipedia$check(paths = c("/","*images/"), bot = "*")
```

## The Functional Style

Retrieving robots.txt file ... 

```{r}
rtxt <- 
  rt_get_robotstxt("wikipedia.org") 

rtxt %>% 
  substring(1,400)
``` 

... extracting permissions ... 

```{r}
rtxt %>% 
  rt_get_permissions() %>% 
  slice(1:10)
``` 

... parsing robots.txt file more general ... 

```{r}
rtxt %>% 
  parse_robotstxt() %>% 
  lapply(head, 2)
``` 

... and checking permissions ... 

```{r}
rtxt %>% 
  rt_get_permissions() %>% 
  paths_allowed(paths=c("/","*images/"), bot="*")
```














