---
title: "README"
author: "Peter Meißner"
date: "`r Sys.time()`"
output: 
  html_document: 
    keep_md: yes
---

```{r, include=FALSE}
library(robotstxt)
```

# Installation and Start

```{r, eval=FALSE}
devtools::install_github("petermeissner/robotstxt")
```



# Dokumentation

```{r}
?robotstxt
```

# Example Usage

Loading the package and magrittr for neater code  ... 

```{r}
library(robotstxt)
library(magrittr)
```

Initializing a new instance of the robotstxt class ... 
```{r}
rt_wikipedia <- robotstxt$new(domain="wikipedia.org")
```


Having a look a some fields (the data stored inside the object) ... 

... the domain for which the permissions apply ... 

```{r}
rt_wikipedia$domain
```

... the actual text of the robots.txt file ... 

```{r}
rt_wikipedia$text %>% 
  substring(1, 400) %>% 
  cat()
```

... bots mentioned by name ...

```{r}
rt_wikipedia$bots
```

Checking if some any bot might access the root path ... 
```{r}
# checking for access permissions
rt_wikipedia$check(path = "/", bot = "*")
```

